The language of generalization: Probability, vagueness, and interaction

### 2018-10-19 paper/comgen-paper.Rmd
clean up elephants and causal task figures; final polish on case study 3

fig.sims.priors <- ggplot(
  bind_rows(sims.priors %>% 
              mutate(src = 'priors'),
            sims.uncertain.thresholds %>% 
              mutate(src = 'posteriors')
            ) %>% mutate(PriorShape = 
                           factor(PriorShape,  
                                  levels = c("barks", "hasSpots", "doesntEatPeople", "laysEggs", "isFemale", "carriesMalaria"),
                            labels = c("bark", "have spots", "don't eat people", "lay eggs", "are female", "carry malaria")),
                         src = factor(src, levels = c("priors", "posteriors"),
                                      labels = c("Prevalence priors", 
                                                 "Interpretation posteriors"))), 
  aes(x = state, fill = PriorShape, color = PriorShape))+
    geom_density(aes(y = ..scaled..), size = 0.6, alpha = 0.7)+
    theme_few() +
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    # geom_rect(data = s1.simulations.relabeled.2,
    #           aes(xmin = featureProb - 0.05, xmax = featureProb + 0.05, ymin = 0.0, ymax = 0.15),
    #           fill = 'black', inherit.aes =F)+
    geom_segment(data = s1.simulations.relabeled.2,
              aes(x = featureProb, xend = featureProb, 
                  yend = 0.02, y = 0.2), size = 1,
              fill = 'black', inherit.aes =F, arrow = arrow(length = unit(0.2, "cm"),
                                                            type = 'open'))+
    geom_label(data = s1.simulations.relabeled.2,
                aes(x = xlabpos, y=0.25, label = category),
                label.padding = unit(0.075, "lines"),
                  family = 'Palatino', fontface = 'bold', size = 3.2, inherit.aes =F, force = 15)+
    ylab("Normalized probability density") +
    xlab("Prevalence")+
    scale_color_solarized()+
    scale_fill_solarized()+
    facet_grid(src~PriorShape, scales = 'free')+
    theme(strip.text.y = element_text(angle = 0, hjust =0),
          legend.position = "none", 
          plot.margin=unit(c(0.5,0.5,1.5,0.5),"cm"))

@@

```{r elephants, fig.cap="Model interpretation of a conjunctive generic (\"Elephants live in Africa and Asia\"). A: Intuitive priors for marginal distributions of prevalence for living in Africa and living in Africa. B: Partial interpretation upon hearing utternace (\"Elephants live in Africa...\"). C: Full interpretation upon hearing the end of the sentence (\"Elephants live in Africa and Asia\"). Uncertainty about the threshold for generic sentences allows the listener to non-monotonoically update its beliefs about the prevalence of the feature in categories.", fig.width = 8, fig.asp = 0.6, out.width = "100%", fig.align = "center", cache=F}
load("cached_results/modelSims-elephants.RData")

fig.eleph.0 <- get_samples(rs.asiaafrica.priors, 10000) %>%
  ggplot(., aes(x = state))+
  geom_density(adjust = 2, fill = 'grey', alpha = 0.3, size = 1.5)+
  facet_wrap(~marginal, ncol = 1)+
  ggtitle('Prevalence priors')+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 1))+
  xlab("")+
  ylab("Probability density")+
  theme(plot.title = element_text(size = 10, hjust = 0.5))

fig.eleph.1 <- get_samples(rs.asia.marignals, 10000) %>%
  ggplot(., aes(x = state))+
  geom_density(adjust = 4, fill = 'grey', alpha = 0.3, size = 1.5)+
  facet_wrap(~marginal, ncol = 1)+
  ggtitle('"Elephants live in Africa..."')+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 1))+
  xlab("Prevalence")+
  ylab("Probability density")+
  theme(axis.title.y = element_blank(),
        plot.title = element_text(size = 10, hjust = 0.5))

fig.eleph.2 <- get_samples(rs.asiaafrica.marignals, 10000) %>%
  ggplot(., aes(x = state))+
  geom_density(adjust = 4, fill = 'grey', alpha = 0.3, size = 1.5)+
  facet_wrap(~marginal, ncol = 1)+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 1))+
  xlab("")+
  ggtitle('"...and Asia"')+
  ylab("Probability density")+
  theme(axis.title.y = element_blank(),
        plot.title = element_text(size = 10, hjust = 0.5))

>>>>

fig.sims.priors <- ggplot(
  bind_rows(sims.priors %>% 
              mutate(src = 'priors'),
            sims.uncertain.thresholds %>% 
              mutate(src = 'posteriors')
            ) %>% mutate(PriorShape = 
                           factor(PriorShape,  
                                  levels = c("barks", "hasSpots", "doesntEatPeople", "laysEggs", "isFemale", "carriesMalaria"),
                            labels = c("bark", "have spots", "don't eat people", "lay eggs", "are female", "carry malaria")),
                         src = factor(src, levels = c("priors", "posteriors"),
                                      labels = c("Prevalence priors", 
                                                 "Interpretation posteriors"))), 
  aes(x = state, fill = PriorShape, color = PriorShape))+
    geom_density(aes(y = ..scaled..), size = 0.6, alpha = 0.7)+
    theme_few() +
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    # geom_rect(data = s1.simulations.relabeled.2,
    #           aes(xmin = featureProb - 0.05, xmax = featureProb + 0.05, ymin = 0.0, ymax = 0.15),
    #           fill = 'black', inherit.aes =F)+
    geom_segment(data = s1.simulations.relabeled.2,
              aes(x = featureProb, xend = featureProb, 
                  yend = 0.02, y = 0.2), size = 1,
              fill = 'black', inherit.aes =F, arrow = arrow(length = unit(0.2, "cm"),
                                                            type = 'open'))+
    geom_label(data = s1.simulations.relabeled.2,
                aes(x = xlabpos, y=0.25, label = category),
                label.padding = unit(0.075, "lines"),
                  family = 'Palatino', fontface = 'bold', size = 3.2, inherit.aes =F, force = 15)+
    ylab("Scaled probability density") +
    xlab("Prevalence")+
    scale_color_solarized()+
    scale_fill_solarized()+
    facet_grid(src~PriorShape, scales = 'free')+
    theme(strip.text.y = element_text(angle = 0, hjust =0),
          legend.position = "none", 
          plot.margin=unit(c(0.5,0.5,1.5,0.5),"cm"))

@@

```{r elephants, fig.cap="Model interpretation of a conjunctive generic (\"Elephants live in Africa and Asia\"). A: Intuitive priors for marginal distributions of prevalence for living in Africa and living in Africa. B: Partial interpretation upon hearing utternace (\"Elephants live in Africa...\"). C: Full interpretation upon hearing the end of the sentence (\"Elephants live in Africa and Asia\"). Uncertainty about the threshold for generic sentences allows the listener to non-monotonoically update its beliefs about the prevalence of the feature in categories.", fig.width = 8, fig.asp = 0.6, out.width = "80%", fig.align = "center", cache=F}
load("cached_results/modelSims-elephants.RData")

fig.eleph.0 <- get_samples(rs.asiaafrica.priors, 10000) %>%
  ggplot(., aes(x = state))+
  geom_density(aes(y = ..scaled..), adjust = 2, fill = 'grey', alpha = 0.3, size = 1.25)+
  facet_wrap(~marginal, ncol = 1)+
  ggtitle('Prevalence priors')+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 1))+
  xlab("")+
  ylab("Scaled probability density")+
  scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
  theme(plot.title = element_text(size = 10, hjust = 0.5))

fig.eleph.1 <- get_samples(rs.asia.marignals, 10000) %>%
  ggplot(., aes(x = state))+
  geom_density(aes(y = ..scaled..), adjust = 4, fill = 'grey', alpha = 0.3, size = 1.25)+
  facet_wrap(~marginal, ncol = 1)+
  ggtitle('"Elephants live in Africa..."')+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 1))+
  scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
  xlab("Prevalence")+
  ylab("Scaled probability density")+
  theme(axis.title.y = element_blank(),
        plot.title = element_text(size = 10, hjust = 0.5))

fig.eleph.2 <- get_samples(rs.asiaafrica.marignals, 10000) %>%
  ggplot(., aes(x = state))+
  geom_density(aes(y = ..scaled..),adjust = 4, fill = 'grey', alpha = 0.3, size = 1.25)+
  facet_wrap(~marginal, ncol = 1)+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 1))+
  scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
  xlab("")+
  ggtitle('"...and Asia"')+
  ylab("Scaled probability density")+
  theme(axis.title.y = element_blank(),
        plot.title = element_text(size = 10, hjust = 0.5),
        axis.ticks.y = element_blank())
